Comparison of FDR methods on GWAS with SummarizedBenchmark

### 2017-10-29 datasets/GWAS/GWAS-SummarizedBenchmark.Rmd
Add ind_covariate to buildBench; run all SNPs

Before moving on, we'll rename the relevant columns so that they will use common terms
across the different datasets. We'll also add a 'test_statistic' column, and subset on a 
toy example before moving on to the full dataset.

```{r, GWAS1-reformat}
bmi <- bmi %>% 
        dplyr::rename(pval = p_value,
               SE = stderr,
               effect_size = effect,
               ind_covariate = N) %>%
        mutate(test_statistic = qnorm(exp(log(pval)-log(2)), lower.tail=FALSE) * sign(effect_size)) %>%
        select(pval, SE, effect_size, ind_covariate, test_statistic)

### experimenting on a subset of the full dataset for now
bmi <- bmi[1:750000,]
```

@@

```{r, GWAS1-sb, results="hide"}
resfile <- paste0(resdir, "bmi_summarizedBenchmark_",
                  nrow(bmi), ".RData")
if (!file.exists(resfile)){
  t1 <- proc.time()
  sb <- bd %>% buildBench(data=bmi, parallel=TRUE, BPPARAM=multicoreParam)
  metadata(sb)$data_download_link <- "http://portals.broadinstitute.org/collaboration/giant/images/3/3a/BMI.SNPadjSMK.zip"
  save(sb, file=resfile)
  message(paste0("Took ", round((proc.time()-t1)[3],1),
                 " seconds for ", nrow(bmi), " SNPs."))
}else{
  load(resfile)
}

```

@@

# Add ind covariate to rowData
rowData(sb)$ind_covariate <- bmi$ind_covariate

>>>>

Before moving on, we'll rename the relevant columns so that they will use common terms
across the different datasets. We'll also add a 'test_statistic' column.

```{r, GWAS1-reformat}
bmi <- bmi %>% 
        dplyr::rename(pval = p_value,
               SE = stderr,
               effect_size = effect,
               ind_covariate = N) %>%
        mutate(test_statistic = qnorm(exp(log(pval)-log(2)), lower.tail=FALSE) * sign(effect_size)) %>%
        select(pval, SE, effect_size, ind_covariate, test_statistic) 
```

@@

```{r, GWAS1-sb, results="hide", message=FALSE}
resfile <- paste0(resdir, "bmi_summarizedBenchmark_",
                  nrow(bmi), ".RData")
if (!file.exists(resfile)){
  t1 <- proc.time()
  sb <- bd %>% buildBench(data=bmi, ftCols = "ind_covariate",
                          parallel=TRUE, BPPARAM=multicoreParam)
  metadata(sb)$data_download_link <- "http://portals.broadinstitute.org/collaboration/giant/images/3/3a/BMI.SNPadjSMK.zip"
  save(sb, file=resfile)
  duration <- round((proc.time()-t1)[3]/60,1)
}else{
  load(resfile)
}
```

This step took `r duration` minutes for `r nrow(bmi)` SNPs using `r cores` cores.

@@
